---
title: "Master's Thesis: Data Analysis"
author: "Brier Gallihugh"
date: "05/24/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Study overview**

This study looked to assess whether various questions related to Christian privilege could be formulated into

This study looked to assess to what extent researcher generated questions pertaining to Christian privilege could be formulated into a scale to assess the construct of Christian Privilege awareness within a US Christian sample. Participants were recruited from Reddit and Eastern Michigan University's SONA system. 

**Reference** These data are from:

Gallihugh, B. (2020). An Exploratory Model of Christian Privilege Awareness. *Journal*, *Vol*(Issue), XX-XX. DOI

**Packages**

pastecs: Normality assumption

GPArotation: Run oblique factor analysis

psych: Run factor analysis

apaTables: Create APA formated tables

foreign: Read SPSS data

readxl: Read Excel Workbooks

```{r Library, message=FALSE}
####Library Loadings####
library(pastecs)
library(GPArotation)
library(psych)
library(apaTables)
library(foreign)
library(readxl)
library(dplyr)
library(psych)
library(car)
library(xtable)
```

```{r dataRaw}
#### Data Input####
MasterData <- read_excel("Master_Clean2.xlsx")
```

**Variables**

Age: The numerical age of participants who are included in the data set

Gender: A categorical variable consisting of several gender identity options (i.e., male, female, trans-male, trans-female, non-binary, etc.)

Religious Beliefs: A categorical variable of self identified Christian identites (i.e., Evangelical, Catholic, Mainline, Other, etc.)

Educational Attainment: A categorical variable of educational attainment (i.e., high school, associates, professional degree, etc.)

Political Affiliation: A continious variable ranging from extremely liberal to extremely conservative.

Christian Privilege Awareness Scale: A 29 item scale looking to assess Christian awarenes of thier own privilege within the United States.

Color-Blind Racial Attitudes Scale: A 20 item scale looking to assess a person's degree of adherence to a "color-blind" ideology (e.g., race does not and should not matter).

Social Dominance Orientation: A 14 item scale looking to assess the degree to which people believe that social hierarchies should exist

Sanctification of Social Justice Scale: A 5 item scale looking to assess the degree to which Christians view striving for social justice is part of their Christian identity.

Religious Fundamentalism Scale: A 12 item scale looking at how religiously fundamental a person's religious beliefs are.

Global Just World Beliefs Scale: A 7 item scale looking to assess the degree to which a person believes that others "get what they deserve and deserve what they get".

Privilege and Oppression Inventory: A 39 item scale looking to assess a person's awareness of White, Christian, Male and Heterosexual privilege.

## Descriptive Information

```{r describe}
####Descriptive Statistics####
Age <- as.numeric(MasterData$DEMO_2)

# Gender w/ Recoded Levels
Gender <- factor(MasterData$DEMO_11, levels = c(1:8), labels = c("Male","Female","Trans-Male","Trans-Female","Non-Binary","Queer/Questioning","Prefer Not To Answer","Other"))

# Religion s/ Recoded Levels
Religion <- factor(MasterData$DEMO_6, levels = c(1:13), labels = c("Evangelical Christian","Judaism","Protestant Christian","Islam","Catholic","Agnostic","Atheist","Other Christian","Hindu","Buddhist","Spiritual","Other Christian","Prefer Not To Answer"))


# Degree w/ Recoded Levels
Degree <- factor(MasterData$DEMO_3, levels = c(1:8), labels = c("Less Than High School","High School Graduate","Some College (No Degree)","Associate's Degree","Bachelor's Degree","Master's Degree","Doctoral Degree","Professional Degree (M.D. or J.D."))

# Race w/ Recoded Levels
Race <- factor(MasterData$DEMO_9, levels = c(1:8), labels = c("White","Black/African American","American Indian or Alaskan Native", "Hispanic/Latino","Asian","Native Hawaiian or Pacific Islander","Other","Other"))

# Political Affiliation
PoliticalAffiliation <- as.numeric(MasterData$DEMO_8)

# Recruitment Site
Recruitment <- factor(MasterData$DEMO_1, levels = c(1:5), labels = c("SONA","Facebook","Twitter","Reddit","Amazon Mechanical Turk"))

#View Relevant Categorical Variables
describe(Age)
summary(Gender)
summary(Religion)
summary(Degree)
summary(Race) # I don't know how to tell R to recognize multi racial groups (43 NA's)
summary(Recruitment)
describe(PoliticalAffiliation)
```

Age had a mean of 26.14 years (SD = 8.58) and had a max and min of 77 and 18 respectively. 

Recruitment took place on SONA (n = 10), Facebook (n = 59), Twitter (n = 1) and Reddit (n = 321).

The gender makeup of the sample consisted of males (n = 249), females (n = 124), trans-males (n = 4), trans-females (n = 2), non-binary (n = 6), non-binary trans/queer (n =1), and Apache Helicopter (n =1). Additionally, 3 selected the "Prefer To Not Answer" option and 1 participant did not respond at all to the question. Overall, this sample included 391 participants. 

Religious ideology of the sample consisted of Evangelical Christians (n = 71), Protestant Christians (n = 166), Catholics (n = 62), and "Other" Christians (n = 92; i.e., )

The educational attainment of the sample consisted of participants who did not complete high school (n =6), completed high school (n = 43), had some college (n = 106), attained an associated degree (n = 31), a bachelors degree (n = 133), a master's degree (n = 49), a doctoral degree (n = 9), or either a J.D. or M.D (n = 14).

The racial makeup of the sample consisted of 289 Whites (n = 289), 14 Blacks or African Americans (n = 14), 28 Hispanic or Latinos (n = 28), 17 Others (n = 17) and many who were of various biracial identities (n = 43). 

```{r Dataframes and Descriptives}
####Key Scales####
#Christian Privilege Scale (Thesis)
ThesisScale <- data.frame(MasterData$Thesis_1,MasterData$Thesis_2,MasterData$Thesis_3,MasterData$Thesis_4,MasterData$Thesis_5,MasterData$Thesis_6,MasterData$Thesis_7,MasterData$Thesis_8,MasterData$Thesis_10,MasterData$Thesis_11,MasterData$Thesis_12,MasterData$Thesis_13,MasterData$Thesis_14,MasterData$Thesis_15,MasterData$Thesis_16,MasterData$Thesis_17,MasterData$Thesis_18,MasterData$Thesis_19,MasterData$Thesis_20,MasterData$Thesis_21,MasterData$Thesis_22,MasterData$Thesis_23,MasterData$Thesis_24,MasterData$Thesis_25,MasterData$Thesis_26,MasterData$Thesis_27,MasterData$Thesis_28,MasterData$Thesis_29)
#Reverse Code Christian Privilege Items
keysThesis <- c(-1,1,1,1,1,-1,-1,1,-1,-1,1,1,1,1,1,-1,-1,-1,-1,1,-1,1,-1,1,1,-1,1,-1)
ThesisScaleReversed <- data.frame(reverse.code(keysThesis,ThesisScale,mini = 1, maxi = 11))
#Rename for Simplicity
colnames(ThesisScaleReversed) <- c("1","2","3","4","5","6","7","8","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29")
ThesisScale <- ThesisScaleReversed
#Create Mean for Christian Privilege (Add To MasterData)
MasterData$ThesisMeanR <- rowMeans(ThesisScaleReversed, na.rm = FALSE, dims = 1L)

# Color-Blind Racial Attitudes Scale (CoBRAS)
COBRA <- data.frame(MasterData$CoBRAS_1,MasterData$CoBRAS_2,MasterData$CoBRAS_3,MasterData$CoBRAS_4,MasterData$CoBRAS_5,MasterData$CoBRAS_6,MasterData$CoBRAS_7,MasterData$CoBRAS_8,MasterData$CoBRAS_9,MasterData$CoBRAS_10,MasterData$CoBRAS_11,MasterData$CoBRAS_12,MasterData$CoBRAS_13,MasterData$CoBRAS_14,MasterData$CoBRAS_15,MasterData$CoBRAS_16,MasterData$CoBRAS_17,MasterData$CoBRAS_18,MasterData$CoBRAS_19,MasterData$CoBRAS_20)
#Reverse Code CoBRAS Items
keysCoBRAS <- c(1,-1,1,-1,-1,-1,1,-1,1,1,-1,-1,1,1,-1,1,-1,1,1,-1)
COBRA <- data.frame(reverse.code(keysCoBRAS,COBRA,mini = 1, maxi = 6))
#Create CoBRAS Scale Mean (Add To Master Data)
MasterData$CoBRASMean <- rowMeans(COBRA, na.rm = FALSE, dims = 1L)

corr.test(MasterData$ThesisMeanR, MasterData$CoBRASMean)


# Social Dominance Orientation Scale (SDO)
SDO <- data.frame(MasterData$SDO_1,MasterData$SDO_2,MasterData$SDO_3,MasterData$SDO_4,MasterData$SDO_5,MasterData$SDO_6,MasterData$SDO_7,MasterData$SDO_8,MasterData$SDO_9,MasterData$SDO_10,MasterData$SDO_11,MasterData$SDO_12,MasterData$SDO_13,MasterData$SDO_14)
#Reverse Code SDO Items
keysSDO <-c(-1,1,1,-1,1,1,-1,1,-1,-1,1,1,-1,-1)
SDO <- data.frame(reverse.code(keysSDO, SDO, mini = , maxi = ))
#Create SDO Scale Mean (Add to Master Data)
MasterData$SDOMean <- rowMeans(SDO, na.rm = FALSE, dims = 1L)


# Christian Fundamentalism Scale (CFS)
CFS <- data.frame(MasterData$CFS_1,MasterData$CFS_2,MasterData$CFS_3,MasterData$CFS_4,MasterData$CFS_5,MasterData$CFS_6,MasterData$CFS_7,MasterData$CFS_8,MasterData$CFS_9,MasterData$CFS_10,MasterData$CFS_11,MasterData$CFS_12)
# Reverse Code CFS Items
keysCFS <- c(1,-1,1,-1,1,1,-1,1,-1,-1,1,-1)
CFS <- data.frame(reverse.code(keysCFS,CFS,mini = 1, maxi = 9))
#Create CFS Scale Mean (Add to Master Data)
MasterData$CFSMean <- rowMeans(CFS, na.rm = FALSE, dims = 1L)


# Global Just World Beliefs Scale (GJWB)
GJWB <- data.frame(MasterData$GJWB_1,MasterData$GJWB_2,MasterData$GJWB_3,MasterData$GJWB_4,MasterData$GJWB_5,MasterData$GJWB_6,MasterData$GJWB_7)
#Create GJWB Scale Mean (Add to Master Data)
MasterData$GJWB_Mean <-rowMeans(GJWB, na.rm = FALSE, dims = 1L)


# Santification of Social Justice Scale (SSJ)
SSJ <- data.frame(MasterData$SSJ_1,MasterData$SSJ_2,MasterData$SSJ_3,MasterData$SSJ_4,MasterData$SSJ_5)
#Create SSJ Scale Mean (Add to Master Data)
MasterData$SSJMean <- rowMeans(SSJ, na.rm = FALSE, dims = 1L)


# Privilege and Oppression Inventory (POI)
POI <- data.frame(MasterData$POI_1,MasterData$POI_2,MasterData$POI_3,MasterData$POI_4,MasterData$POI_5,MasterData$POI_6,MasterData$POI_7,MasterData$POI_8,MasterData$POI_9,MasterData$POI_10,MasterData$POI_11,MasterData$POI_12,MasterData$POI_13,MasterData$POI_14,MasterData$POI_15,MasterData$POI_16,MasterData$POI_17,MasterData$POI_18,MasterData$POI_19,MasterData$POI_20,MasterData$POI_21,MasterData$POI_22,MasterData$POI_23,MasterData$POI_24,MasterData$POI_25,MasterData$POI_26,MasterData$POI_27,MasterData$POI_28,MasterData$POI_29,MasterData$POI_30,MasterData$POI_31,MasterData$POI_32,MasterData$POI_33,MasterData$POI_34,MasterData$POI_35,MasterData$POI_36,MasterData$POI_37,MasterData$POI_38,MasterData$POI_39)
# Reverse Code POI Items
keysPOI <- c(1,1,1,-1,1,1,1,1,1,1,1,1,1,1,1,-1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
POI <- data.frame(reverse.code(keysPOI,POI,mini = 1, maxi = 6))
#Create POI Scale Mean (Add to Master Data)
MasterData$POIMean <- rowMeans(POI, na.rm = FALSE, dims = 1L)




#Create POI White Subscale
POIWhite <- data.frame(POI$MasterData.POI_2, POI$MasterData.POI_5, POI$MasterData.POI_13, POI$MasterData.POI_14, POI$MasterData.POI_16., POI$MasterData.POI_24, POI$MasterData.POI_26, POI$MasterData.POI_27, POI$MasterData.POI_29, POI$MasterData.POI_32, POI$MasterData.POI_33, POI$MasterData.POI_38, POI$MasterData.POI_39)
#Create POI White Mean
MasterData$POIWhiteMean <- rowMeans(POIWhite,na.rm = FALSE, dims = 1L)
#Create POI Christian Subscale
POIChristian <- data.frame(POI$MasterData.POI_1, POI$MasterData.POI_3, POI$MasterData.POI_8, POI$MasterData.POI_11, POI$MasterData.POI_12, POI$MasterData.POI_20, POI$MasterData.POI_22, POI$MasterData.POI_36)
describe(POIChristian)
#Create Mean POI Christian
MasterData$POIChristianMean <- rowMeans(POIChristian,na.rm = FALSE, dims = 1L)
```

```{r descriptives}
####Scale Descriptive Statistics####
#Christian Privilege Descriptives
describe(ThesisScaleReversed)
describe(MasterData$ThesisMeanR)
#SSJ Descriptives
describe(SSJ)
describe(MasterData$SSJMean)
#SDO Descriptives
describe(SDO)
describe(MasterData$SDOMean)
#POI Descriptives
describe(POI)
describe(MasterData$POIMean)
#GJWB Desriptives
describe(GJWB)
describe(MasterData$GJWB_Mean)
#CoBRAS Descriptives
describe(COBRA)
describe(MasterData$CoBRASMean)
#CFS Descriptives
describe(CFS)
describe(MasterData$CFSMean)
```

The Christian Privilege Awareness Scale had 28 items with item means ranging between 4.87 and 9.50 (*SD* = 2.19 to *SD* 3.60). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 7.55, *SD* = 1.52).

The Santification of Social Justice Scale had 5 items with item means ranging between 4.02 and 5.61 (*SD* = 1.62 to *SD* = 2.10). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 5.05, *SD* = 1.62).

The Social Dominance Orientation had 14 items with item means ranging between 1.44 and 2.10 (*SD* = 0.90 to *SD* = 2.18). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 2.34, *SD* = 1.11).

The Privilege and Oppression Inventory had 39 items with item means ranging between 2.94 and 5.24 (*SD* = 0.97 to *SD* = 1.91). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 4.11, *SD* = 1.17).

The Global Just World Beliefs Scale had 7 items with item means ranging between 2.14 and 3.75 (*SD* = 1.17 to *SD* = 1.36). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 2.82, *SD* = 0.94).

The CoBRAS had 20 items with item means ranging between 1.66 and 3.67 (*SD* = 0.99 to *SD* = 1.82). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 2.80, *SD* = 1.17).

The Religious Fundamentalism Scale had 12 items with item means ranging between 4.23 and 6.87 (*SD* = 2.36 to *SD* = 2.96). Scores indicate that the average participant rated their responses from "xx" to "xx" (*M* = 5.51, *SD* = 1.99).

```{r Graphical Data}
####Graphical Data####
#Graphical Data (Histograms)
#Item 1
hist((ThesisScale$`1`),
     xlab = "Item 1",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`1`, na.rm=TRUE), 
            sd = sd(ThesisScale$`1`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 2
hist((ThesisScale$`2`),
     xlab = "Item 2",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`2`, na.rm=TRUE), 
            sd = sd(ThesisScale$`2`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 3
hist((ThesisScale$`3`),
     xlab = "Item 3",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`3`, na.rm=TRUE), 
            sd = sd(ThesisScale$`3`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 4
hist((ThesisScale$`4`),
     xlab = "Item 4",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`4`, na.rm=TRUE), 
            sd = sd(ThesisScale$`4`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 5
hist((ThesisScale$`5`),
     xlab = "Item 5",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`5`, na.rm=TRUE), 
            sd = sd(ThesisScale$`5`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 6
hist((ThesisScale$`6`),
     xlab = "Item 6",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`6`, na.rm=TRUE), 
            sd = sd(ThesisScale$`6`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 7
hist((ThesisScale$`7`),
     xlab = "Item 7",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`7`, na.rm=TRUE), 
            sd = sd(ThesisScale$`7`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 8
hist((ThesisScale$`8`),
     xlab = "Item 8",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`8`, na.rm=TRUE), 
            sd = sd(ThesisScale$`8`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 10
hist((ThesisScale$`10`),
     xlab = "Item 10",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`10`, na.rm=TRUE), 
            sd = sd(ThesisScale$`10`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 11
hist((ThesisScale$`11`),
     xlab = "Item 11",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`11`, na.rm=TRUE), 
            sd = sd(ThesisScale$`11`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 12
hist((ThesisScale$`12`),
     xlab = "Item 12",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`12`, na.rm=TRUE), 
            sd = sd(ThesisScale$`12`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 13
hist((ThesisScale$`13`),
     xlab = "Item 13",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`13`, na.rm=TRUE), 
            sd = sd(ThesisScale$`13`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 14
hist((ThesisScale$`14`),
     xlab = "Item 14",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`14`, na.rm=TRUE), 
            sd = sd(ThesisScale$`10`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 15
hist((ThesisScale$`15`),
     xlab = "Item 15",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`15`, na.rm=TRUE), 
            sd = sd(ThesisScale$`10`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 16
hist((ThesisScale$`16`),
     xlab = "Item 16",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`16`, na.rm=TRUE), 
            sd = sd(ThesisScale$`16`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 17
hist((ThesisScale$`17`),
     xlab = "Item 17",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`17`, na.rm=TRUE), 
            sd = sd(ThesisScale$`17`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 18
hist((ThesisScale$`18`),
     xlab = "Item 18",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`18`, na.rm=TRUE), 
            sd = sd(ThesisScale$`18`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 19
hist((ThesisScale$`19`),
     xlab = "Item 19",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`19`, na.rm=TRUE), 
            sd = sd(ThesisScale$`19`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 20
hist((ThesisScale$`20`),
     xlab = "Item 20",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`20`, na.rm=TRUE), 
            sd = sd(ThesisScale$`20`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 21
hist((ThesisScale$`21`),
     xlab = "Item 21",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`21`, na.rm=TRUE), 
            sd = sd(ThesisScale$`21`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 22
hist((ThesisScale$`22`),
     xlab = "Item 22",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`22`, na.rm=TRUE), 
            sd = sd(ThesisScale$`22`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 23
hist((ThesisScale$`23`),
     xlab = "Item 20",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`23`, na.rm=TRUE), 
            sd = sd(ThesisScale$`23`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 24
hist((ThesisScale$`24`),
     xlab = "Item 24",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`24`, na.rm=TRUE), 
            sd = sd(ThesisScale$`24`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 25
hist((ThesisScale$`25`),
     xlab = "Item 25",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`25`, na.rm=TRUE), 
            sd = sd(ThesisScale$`25`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 26
hist((ThesisScale$`26`),
     xlab = "Item 26",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`26`, na.rm=TRUE), 
            sd = sd(ThesisScale$`26`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 27
hist((ThesisScale$`27`),
     xlab = "Item 27",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`27`, na.rm=TRUE), 
            sd = sd(ThesisScale$`27`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 28
hist((ThesisScale$`28`),
     xlab = "Item 28",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`28`, na.rm=TRUE), 
            sd = sd(ThesisScale$`28`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Item 29
hist((ThesisScale$`29`),
     xlab = "Item 29",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(ThesisScale$`29`, na.rm=TRUE), 
            sd = sd(ThesisScale$`29`, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
```

## Statistical assumptions
```{r statistical assumptions}
####Statistical Assumptions####

#Create Correlation Matrix for Thesis Scale
corThesisScale <- cor(ThesisScaleReversed, use = "pairwise.complete.obs")
#View Correlation Table for Thesis Scale
corThesisScale
#Create APA Correlation Table for DOC Export
apa.cor.table(corThesisScale, filename="ThesisScaleCorrelations.doc", landscape = TRUE, show.conf.interval = FALSE)

# Analyze Correlation Matrix

# #1 => 5 Items correlated > .80 (Remove)
# #4,8,13 => At least half (14) of correlations < .30 (Remove)
ThesisScale_Revised <- data.frame(ThesisScaleReversed$`2`,ThesisScaleReversed$`3`,ThesisScaleReversed$`5`,ThesisScaleReversed$`6`,ThesisScaleReversed$`7`,ThesisScaleReversed$`10`,ThesisScaleReversed$`11`,ThesisScaleReversed$`12`,ThesisScaleReversed$`14`,ThesisScaleReversed$`15`,ThesisScaleReversed$`16`,ThesisScaleReversed$`17`,ThesisScaleReversed$`18`,ThesisScaleReversed$`19`,ThesisScaleReversed$`20`,ThesisScaleReversed$`21`,ThesisScaleReversed$`22`,ThesisScaleReversed$`23`,ThesisScaleReversed$`24`,ThesisScaleReversed$`25`,ThesisScaleReversed$`26`,ThesisScaleReversed$`27`,ThesisScaleReversed$`28`,ThesisScaleReversed$`29`)
#Rename for Simplicity
colnames(ThesisScale_Revised) <- c("2","3","5","6","7","10","11","12","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29")

corThesis_Revised <- cor(ThesisScale_Revised, use = "pairwise.complete.obs")

#Barlett Test for Thesis Scale (n = # of observations)
cortest.bartlett(corThesis_Revised, n = 389)

#KMO for New Scale
KMO(corThesis_Revised)

#Determinent for New Scale
det(corThesis_Revised)

#Add Mean
MasterData$ThesisScale_RevisedMean <- rowMeans(ThesisScale_Revised, na.rm = FALSE, dims = 1L)


#Histogram of Thesis Mean Scores
hist((MasterData$ThesisScale_RevisedMean),
     xlab = "Thesis Revised Mean",
     main = "",
     col = 'palegreen',
     probability = TRUE)
curve(dnorm(x, mean = mean(MasterData$ThesisScale_RevisedMean, na.rm=TRUE), 
            sd = sd(MasterData$ThesisScale_RevisedMean, na.rm=TRUE)), 
            add = TRUE, lwd = 2)
#Thesis Mean Statistical Data (Skew/Kurtosis)
describe(MasterData$ThesisScale_RevisedMean)
shapiro.test(MasterData$ThesisScale_RevisedMean)
```

The bi variate correlations appear to be reasonably highly correlated therefore meeting the assumption.

The homogeneity assumption was assessed using Bartlett test. It was found that the assumption was met with p < .001.

Sample size appears to be met as the KMO for the overall measure is .93. Additonally the Bartlett test shows there is not a multicollinearity issue with p > .00006. 

The normality assumption appears to be violated. A Shapiro Wilks test confirms that the normality assumption has been violated, *p* < .001.

## Statistical Analyses
```{r Thesis Scale Analysis}
####Initial Scree Plot and Parallel Analysis####
# Create Scree Plot (+/- 1; Use both Orthogonal and Oblique)
# Scree Plot FA suggests 4 factor solution
scree(corThesis_Revised)

# Assess Number of Factors (Analyze +/- 1 on both Orthogonal and Oblique)
fa.parallel(corThesis_Revised, n.obs = 389, n.iter = 1000) #Suggests 4 Factor Solution
```

```{r Thesis Scale Orthogonal 3,4,5}
####Initial Orthogonal Factor Analysis####

#Item Retention Criteria (Worthington, et al., 2005)
#Cross Loading: Factor Difference less than .15
#Items Deletion: Highest Factor Loading < .32
#Item Deletion: Items with +2 Factor Loadings > .32

# Orthogonal Analysis (3 Factor)
Ortho3 <- fa(r = corThesis_Revised, nfactors = 3,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho3, sort = TRUE)
#Show Loading Structure
print.psych(Ortho3, sort = TRUE)
#Items to Delete: 26, 14, 17

# Orthogonal Analysis (4 Factor) NOPE TOO MANY FACTOR CROSS LOADINGS
Ortho4 <- fa(r = corThesis_Revised, nfactors = 4,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho4, sort = TRUE)
#Show Loading Structure
print.psych(Ortho4, sort = TRUE)
#Items to Delete: 6, 27, 25, 19, 18, 5, 16, 26, 24, 15, 20, 14, 17

# Orthogonal Analysis (5 Factor)
Ortho5 <- fa(r = corThesis_Revised, nfactors = 5,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho5, sort = TRUE)
#Show Loading Structure
print.psych(Ortho5, sort = TRUE)
#Items to Delete: 6, 27, 25, 16, 19, 24, 18, 23, 14, 17

# Orthogonal Analysis (2 Factor)
Ortho2 <- fa(r = corThesis_Revised, nfactors = 2,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho2, sort = TRUE)
#Show Loading Structure
print.psych(Ortho2, sort = TRUE)
# Items To Delete: 26, 15, 17, 3, 14

# THE THREE FACTOR ORTHONGONAL IS BEST INITIAL FIT W/ 3 CROSS LOADINGS 
# 14 AND 17 CROSS LOAD IN EACH SOLUTION
# CONSIDER DELETION OF BOTH
```

```{r Thesis Scale Oblique 3,4,5}
####Initial Oblique Factor Analysis####

# Oblique Analysis (3 Factor)
Oblique3 <- fa(r = corThesis_Revised, nfactors = 3,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique3, sort = TRUE)
#Show Loading Structure
print.psych(Oblique3, sort = TRUE)
#Item Deletion: 15, 14, 2, 17

# Oblique Analysis (4 Factor)
Oblique4 <- fa(r = corThesis_Revised, nfactors = 4,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique4, sort = TRUE)
#Show Loading Structure
print.psych(Oblique4, sort = TRUE)
#Item Deletions: 25, 14, 27, 19, 18, 12, 17

# Oblique Analysis (5 Factor)
Oblique5 <- fa(r = corThesis_Revised, nfactors = 5,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique5, sort = TRUE)
#Show Loading Structure
print.psych(Oblique5, sort = TRUE)
#Item Deletion: 19, 18, 14, 27, 25, 23, 2, 17

# Oblique Analysis (2 Factor)
Oblique2 <- fa(r = corThesis_Revised, nfactors = 2,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique2, sort = TRUE)
#Show Loading Structure
print.psych(Oblique2, sort = TRUE)
#Items Deletion: 17, 3, 14


# TTWO FACTOR OBLIQUE IS BEST OBLIQUE SOLUTION
# 17 AND 14 CROSS LOAD IN EACH SOLUTION)
# CONSIDER DELETING THEM
```

```{r Thesis Scale Secondary Analysis}
####Secondary Scree and Parallel Analysis####

#Common Cross Loadings with #14 and #17 are pretty consistent among all rotations and potential solutions. Eliminate these items

#Try without #14 and #17

ThesisScale_Revised2 <- data.frame(ThesisScaleReversed$`2`,ThesisScaleReversed$`3`,ThesisScaleReversed$`5`,ThesisScaleReversed$`6`,ThesisScaleReversed$`7`,ThesisScaleReversed$`10`,ThesisScaleReversed$`11`,ThesisScaleReversed$`12`,ThesisScaleReversed$`15`,ThesisScaleReversed$`16`,ThesisScaleReversed$`18`,ThesisScaleReversed$`19`,ThesisScaleReversed$`20`,ThesisScaleReversed$`21`,ThesisScaleReversed$`22`,ThesisScaleReversed$`23`,ThesisScaleReversed$`24`,ThesisScaleReversed$`25`,ThesisScaleReversed$`26`,ThesisScaleReversed$`27`,ThesisScaleReversed$`28`,ThesisScaleReversed$`29`)


#Rename for Simplicity
colnames(ThesisScale_Revised2) <- c("2","3","5","6","7","10","11","12","15","16","18","19","20","21","22","23","24","25","26","27","28","29")

corThesis_Revised2 <- cor(ThesisScale_Revised2, use = "pairwise.complete.obs")

#Re-Check Normality

MasterData$MeanR2 <- rowMeans(ThesisScale_Revised2, na.rm = FALSE, dims = 1L)
describe(MasterData$MeanR2)
hist(MasterData$MeanR2)

#Barlett Test for Thesis Scale (n = # of observations)
cortest.bartlett(corThesis_Revised2, n = 389)

#KMO for New Scale
KMO(corThesis_Revised2)

#Determinent for New Scale
det(corThesis_Revised2)

# Create Scree Plot (+/- 1; Use both Orthogonal and Oblique)
# Scree Plot FA suggests 3 factor solution
scree(corThesis_Revised2)

# Assess Number of Factors (Analyze +/- 1 on both Orthogonal and Oblique)
fa.parallel(corThesis_Revised2, n.obs = 389, n.iter = 1000) #Suggests 4 Factor Solution
```

Ended here @ 5:20pm 12/18/20

```{r Thesis Secondary Analysis Orthogonal}
####Secondary Orthogonal Factor Analysis####

# Orthogonal Analysis (3 Factor)
Ortho3R <- fa(r = corThesis_Revised2, nfactors = 3,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho3R, sort = TRUE)
#Show Loading Structure
print.psych(Ortho3R, sort = TRUE)
#Item Deletion: 26, 3

# Orthogonal Analysis (4 Factor)
Ortho4R <- fa(r = corThesis_Revised2, nfactors = 4,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho4R, sort = TRUE)
#Show Loading Structure
print.psych(Ortho4R, sort = TRUE)
#Item Deletion: 26, 27, 25, 19, 18, 11, 10, 29, 6, 22, 2

# Orthogonal Analysis (5 Factor)
Ortho5R <- fa(r = corThesis_Revised2, nfactors = 5,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho5R, sort = TRUE)
#Show Loading Structure
print.psych(Ortho5R, sort = TRUE)
#Item Deletions: 26, 24, 27, 19, 25, 18, 11, 29, 6, 22, 23, 2

# Orthogonal Analysis (2 Factor)
Ortho2R <- fa(r = corThesis_Revised2, nfactors = 2,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho2R, sort = TRUE)
#Show Loading Structure
print.psych(Ortho2R, sort = TRUE)
## Item Deletions: 26, 21, 3

# ORTHOGONAL 3 FACTOR SOLUTION BEST

## 26 CROSS LOADS ON EACH SOLUTION (3, 4 AND 5; ALSO ON 2 FACTOR)
```

```{r Thesis Secondary Analysis Oblique}
####Secondary Oblique Factor Analysis####

# Oblique Analysis (3 Factor)
Oblique3R <- fa(r = corThesis_Revised2, nfactors = 3,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique3R, sort = TRUE)
#Show Loading Structure
print.psych(Oblique3R, sort = TRUE)
#Item Deletions: 3

# Oblique Analysis (4 Factor)
Oblique4R <- fa(r = corThesis_Revised2, nfactors = 4,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique4R, sort = TRUE)
#Show Loading Structure
print.psych(Oblique4R, sort = TRUE)
#Item Deletion: 27, 25, 19, 18, 12

# Oblique Analysis (5 Factor)
Oblique5R <- fa(r = corThesis_Revised2, nfactors = 5,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique5R, sort = TRUE)
#Show Loading Structure
print.psych(Oblique5R, sort = TRUE)
#Item Deletion: 27, 19, 18, 23

# Oblique Analysis (2 Factor)
Oblique2R <- fa(r = corThesis_Revised2, nfactors = 2,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique2R, sort = TRUE)
#Show Loading Structure
print.psych(Oblique2R, sort = TRUE)
#Item Deletion: 3

# 3 FACTOR OBLIQUE IS BEST OVERALL SOLUTION BASED ON NEW CROSS LOADING AND CUMULATIVE VARIANE EXPLAINED. HOWEVER, REMOVE #3 (CROSS AND HANGING ITEM)
```

```{r Thesis Tertiary Analysis}
####Tertiary Scree Plot and Parallel Analysis####

#Take Out #3
ThesisScale_Revised3 <- data.frame(ThesisScaleReversed$`2`,ThesisScaleReversed$`5`,ThesisScaleReversed$`6`,ThesisScaleReversed$`7`,ThesisScaleReversed$`10`,ThesisScaleReversed$`11`,ThesisScaleReversed$`12`,ThesisScaleReversed$`15`,ThesisScaleReversed$`16`,ThesisScaleReversed$`18`,ThesisScaleReversed$`19`,ThesisScaleReversed$`20`,ThesisScaleReversed$`21`,ThesisScaleReversed$`22`,ThesisScaleReversed$`23`,ThesisScaleReversed$`24`,ThesisScaleReversed$`25`,ThesisScaleReversed$`26`,ThesisScaleReversed$`27`,ThesisScaleReversed$`28`,ThesisScaleReversed$`29`)

#Create Mean
MasterData$FinalThesisMean <- rowMeans(ThesisScale_Revised3, na.rm = FALSE, dims = 1L)


#Rename for Simplicity
colnames(ThesisScale_Revised3) <- c("2","5","6","7","10","11","12","15","16","18","19","20","21","22","23","24","25","26","27","28","29")

corThesis_Revised3 <- cor(ThesisScale_Revised3, use = "pairwise.complete.obs")

#Re-Check Normality

MasterData$MeanR3 <- rowMeans(ThesisScale_Revised3, na.rm = FALSE, dims = 1L)
psych::describe(MasterData$MeanR3)
hist(MasterData$MeanR3)

#Barlett Test for Thesis Scale (n = # of observations)
cortest.bartlett(corThesis_Revised3, n = 391)

#KMO for New Scale
KMO(corThesis_Revised3)

#Determinent for New Scale
det(corThesis_Revised3)

# Create Scree Plot (+/- 1; Use both Orthogonal and Oblique)
# Scree Plot FA suggests 3 factor solution
scree(corThesis_Revised3)

# Assess Number of Factors (Analyze +/- 1 on both Orthogonal and Oblique)
fa.parallel(corThesis_Revised3, n.obs = 389, n.iter = 1000) #Suggests 3 Factor Solution
```



```{r Thesis Tertiary Analysis Orthogonal}
####Tertiary Orthogonal Factor Analysis####

# Orthogonal Analysis (2 Factor)
Ortho2R3 <- fa(r = corThesis_Revised3, nfactors = 2,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho2R3, sort = TRUE)
#Show Loading Structure
print.psych(Ortho2R3, sort = TRUE)
#Item Deletion: 26

# Orthogonal Analysis (3 Factor)
Ortho3R3 <- fa(r = corThesis_Revised3, nfactors = 3,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho3R3, sort = TRUE)
#Show Loading Structure
print.psych(Ortho3R3, sort = TRUE)
#Item Deletion: 26, 24, 27, 25, 19, 18, 11, 29, 22, 6

# Orthogonal Analysis (4 Factor)
Ortho4R3 <- fa(r = corThesis_Revised3, nfactors = 4,rotate = 'varimax', use = "pairwise.complete.obs")
#Show All Info
print(Ortho4R3, sort = TRUE)
#Show Loading Structure
print.psych(Ortho4R3, sort = TRUE)
#Item Deletions: 26, 24, 27, 25,19, 18, 11, 6, 29, 22
```



```{r Thesis Tertiary Analysis Oblique}
####Tertiary Oblique Factor Analysis####

# Oblique Analysis (2 Factor) *BEST OVERALL SOLUTION FOR DATA*
Oblique2R3 <- fa(r = corThesis_Revised3, nfactors = 2,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique2R3, sort = TRUE)
#Show Loading Structure
print.psych(Oblique2R3, sort = TRUE)
#Item Deletions: NONE

# Oblique Analysis (3 Factor)
Oblique3R3 <- fa(r = corThesis_Revised3, nfactors = 3,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique3R3, sort = TRUE)
#Show Loading Structure
print.psych(Oblique3R3, sort = TRUE)
#Item Deletion: 27, 25, 19, 18

# Oblique Analysis (4 Factor)
Oblique4R3 <- fa(r = corThesis_Revised3, nfactors = 4,rotate = 'oblimin', use = "pairwise.complete.obs")
#Show All Info
print(Oblique4R3, sort = TRUE)
#Show Loading Structure
print.psych(Oblique3R3, sort = TRUE)
#Item Deletion: 27, 25, 19, 18
```



```{r Normality Assumption for Standard Residuals New Scale}
####Normality Assumption (Residuals)####

#Run for Decided Upon Factor Structure Solution (2 Oblique Looks Best)

# Create Standard Residuals 
Residuals <- scale(Oblique2R3$residual)

# Test Normality of Standard Residuals (Quantitatively)
shapiro.test(Residuals)

# Test Normality of Standard Residuals (Graphically)
hist(Residuals, col = 'lightgrey', 
     main="", xlab = "EFA Model Residuals, FA = 2 (Oblique)",
    probability = TRUE)
 curve(dnorm(x, mean = mean(Residuals), 
            sd = sd(Residuals)), 
           add = TRUE, lwd = 2, col = 'blue')
 
 describe(Residuals)
```



```{r Reliability}
####Scale Reliability####

#Factors
Factor1<- c("27","16","6","11","24","5","22","25","29","19","26","10","20","18","15","7")
Factor2<- c("12","28","21","2","23")

Overall <- c("27","16","6","11","24","5","22","25","29","19","26","10","20","18","15","7","12","28","21","2","23")

#Reliablity Factor 1 ($\alpha$ = .92)
psych::alpha(ThesisScale_Revised3[, Factor1])
#Reliability Factor 2 ($\alpha$ = .74)
psych::alpha(ThesisScale_Revised3[, Factor2])
#Overall Reliability ($\alpha$ = .91)
psych::alpha(ThesisScale_Revised3[, Overall], check.keys = TRUE)

psych::describe(ThesisScale_Revised3)

Thesis_Factor1 <- data.frame(ThesisScaleReversed$`5`,ThesisScaleReversed$`6`,ThesisScaleReversed$`7`,ThesisScaleReversed$`10`,ThesisScaleReversed$`11`,ThesisScaleReversed$`15`,ThesisScaleReversed$`16`,ThesisScaleReversed$`18`,ThesisScaleReversed$`19`,ThesisScaleReversed$`20`,ThesisScaleReversed$`22`,ThesisScaleReversed$`24`,ThesisScaleReversed$`25`,ThesisScaleReversed$`26`,ThesisScaleReversed$`27`,ThesisScaleReversed$`29`)

Thesis_Factor2 <- data.frame(ThesisScaleReversed$`2`,ThesisScaleReversed$`12`,ThesisScaleReversed$`28`,ThesisScaleReversed$`21`,ThesisScaleReversed$`23`)

MasterData$Factor1Mean <- rowMeans(Thesis_Factor1, na.rm = FALSE, dims = 1L)
MasterData$Factor2Mean <- rowMeans(Thesis_Factor2, na.rm = FALSE, dims = 1L)
    
```

The overall reliability was $\alpha$ = .91, 95% CI [.90,.92]

The reliability of Factor 1 (Societal Privilege) was $\alpha$ = .92, 95% CI [.90,.93].

Reliability of Factor 2 (Personal Privilege) was $\alpha$ = .74, 95% CI [.69,.78]

```{r Output Validity}
####Output Validity Measures####



#Thesis, POIWhite, CoBRAS, SDO, RF, GJWB
Output_Validity <- data.frame(MasterData$Factor1Mean, MasterData$Factor2Mean, MasterData$FinalThesisMean, MasterData$POIChristianMean, MasterData$POIWhiteMean, MasterData$CoBRASMean, MasterData$GJWB_Mean, MasterData$SDOMean, MasterData$CFSMean, MasterData$SSJMean)
#Create Labels
colnames(Output_Validity) <- c("CPAS: Christian Exceptionalism","CPAS: Freedom from Discrimination","CPAS: Total Score","POI: Christian", "POI: White","COBRAS","GJWB","SDO","RF","SSJ")
#Correlation Table
corr.test(Output_Validity, y = NULL, use = "pairwise", method = "pearson",adjust = "holm", alpha = 0.05, ci = TRUE, minlength = 5)
#APA Formatted Table
apa.cor.table(Output_Validity,filename = "WithError.doc",show.conf.interval = TRUE, landscape = TRUE)

#Created Without Error 
MasterData1 <- data.frame(filter(MasterData, MasterData$POI_Include > 0))
#Thesis, POIWhite, CoBRAS, SDO, RF, GJWB
Output_Validity <- data.frame(MasterData1$Factor1Mean, MasterData1$Factor2Mean, MasterData1$FinalThesisMean, MasterData1$POIChristianMean, MasterData1$POIWhiteMean, MasterData1$CoBRASMean, MasterData1$GJWB_Mean, MasterData1$SDOMean, MasterData1$CFSMean)
#Create Labels
colnames(Output_Validity) <- c("CPAS: Christian Exceptionalism","CPAS: Freedom from Discrimination","CPAS: Total Score","POI: Christian", "POI: White","COBRAS","GJWB","SDO","RF")
#Correlation Table
corr.test(Output_Validity, y = NULL, use = "pairwise", method = "pearson",adjust = "holm", alpha = 0.05, ci = TRUE, minlength = 5)
#APA Formatted Table
apa.cor.table(Output_Validity,filename = "WithoutError.doc",show.conf.interval = TRUE, landscape = TRUE)
```

```{r Concurrent Validity}
####Concurrent Validity Measures####
#Thesis, POIWhite, CoBRAS, SDO, RF, GJWB
Concurrent_Validity <- data.frame(MasterData$Factor1Mean, MasterData$Factor2Mean, MasterData$FinalThesisMean, MasterData$POIWhiteMean, MasterData$CoBRASMean, MasterData$GJWB_Mean, MasterData$SDOMean, MasterData$CFSMean, MasterData$SSJMean)
#Create Labels
colnames(Concurrent_Validity) <- c("CPAS: Christian Exceptionalism","CPAS: Freedom from Discrimination","CPAS: Total Score","POI: White","COBRAS","GJWB","SDO","RF", "Sanctification for Social Justice")
#Correlation Table
corr.test(Concurrent_Validity, y = NULL, use = "pairwise", method = "pearson",adjust = "holm", alpha = 0.05, ci = TRUE, minlength = 5)
#APA Formatted Table
apa.cor.table(Concurrent_Validity,filename = "APAConcurrentValidity.doc",show.conf.interval = TRUE, landscape = TRUE)
```


```{r Convergent Validity}
####Convergent Validity Measures####
#Thesis, POIChristian, SSJ
Convergent_Validity <- data.frame(MasterData$Factor1Mean, MasterData$Factor2Mean,
 MasterData$FinalThesisMean, MasterData$POIChristianMean, MasterData$SSJMean)
#Create Labels
colnames(Convergent_Validity) <- c("CPAS: Christian Exceptionalism","CPAS: Freedom from Discrimination","CPAS: Total Score","POI: Christian", "Sanctification for Social Justice")
#Correlation Table
corr.test(Convergent_Validity, y = NULL, use = "pairwise", method = "pearson",adjust = "holm", alpha = 0.05, ci = TRUE, minlength = 5)
#APA Formatted Table
apa.cor.table(Convergent_Validity,filename = "APAConvergentValidity.doc",show.conf.interval = TRUE, landscape = TRUE)

#POI Sub Correlations
POI_Correlation <- data.frame(MasterData$POIChristianMean,MasterData$POIWhiteMean)
corr.test(POI_Correlation, y = NULL, use = "pairwise", method = "pearson",adjust = "holm", alpha = 0.05, ci = TRUE, minlength = 5)
library(psych)
library(apaTables)
```

```{r correlation tests}
#COBRA
psych::corr.test(MasterData$POIChristianMean, MasterData$Factor1Mean)
psych::corr.test(MasterData$POIChristianMean, MasterData$CoBRASMean)
psych::corr.test(MasterData$Factor1Mean, MasterData$CoBRASMean)
#COBRA
psych::r.test(n = 380,-.73,-.83,n2 = 383) #Statistically different (correct)


#SDO
psych::corr.test(MasterData$POIChristianMean, MasterData$SDOMean)
psych::corr.test(MasterData$Factor1Mean, MasterData$SDOMean)
#SDO
psych::r.test(n = 380,-.58,-.71,n2 = 382) #Statistically different (correct)

#POI White
psych::corr.test(MasterData$POIChristianMean, MasterData$POIWhiteMean)
psych::corr.test(MasterData$Factor1Mean, MasterData$POIWhiteMean)
#POI White
psych::r.test(n = 374,.78,.79,n2 = 376) #NS (correct)

#GJWB
psych::corr.test(MasterData$POIChristianMean, MasterData$GJWB_Mean)
psych::corr.test(MasterData$Factor1Mean, MasterData$GJWB_Mean)
#GJWB
psych::r.test(n = 382,-.35,-.47,n2 = 385) #NS?? (correct)

#RF
psych::corr.test(MasterData$POIChristianMean, MasterData$CFSMean)
psych::corr.test(MasterData$Factor1Mean, MasterData$CFSMean)
#RF
psych::r.test(n = 380,-.52,-.64,n2 = 383) #Statistically different (not correct)

#SSJ
psych::corr.test(MasterData$POIChristianMean, MasterData$SSJMean)
psych::corr.test(MasterData$Factor1Mean, MasterData$SSJMean)
#RF
psych::r.test(n = 382,.57,.61,n2 = 385) #NS (correct)












```

